Convex Surrogates via Polyhedral Losses

### 2019-01-31 cvx-fin.tex
added empty intro section; started defs

\section{Setting and Background}

>>>>

\section{Introduction}

\section{Setting and Background}
There is a finite outcome space $|\Y|$ with $|\Y|=n$.
The set of distributions on $\Y$ is $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.

We study the minimization of \emph{loss functions} of the form $\ell: \R \to \reals^{\Y}_+$.
The abstract set $\R$ is the \emph{report space}, $\ell(r)$ is a vector specifying the loss of report $r$ on all outcomes, and $\ell(r)_y \in \reals_+$ is the loss of $r$ when outcome $y$ is observed.
The expected loss of report $r$ when $y \sim p$ is written $\langle p, \ell(r) \rangle$.
